|

### 2025-07-16 output/IMPS-2025-slideshow.qmd
Correct html tags in latent space options

:::::::::::::::::::::::::::::::::::::::: columns
::::::::::::::::::::::::::::::::::::::: {.column width="33%"}
<center>

A?`<`{=html}
`/center>`{=html}

@@

rot_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```

:::

:::::::::::::::::::::::::::::::::::::: {.column width="33%"}
<center>

B?`<`{=html}
`/center>`{=html}

@@

ts_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```

:::

::::::::::::::::::::::::::::::::::::: {.column width="33%"}
<center>

C?`<`{=html}
`/center>`{=html}

@@

ls_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```

:::

::::::

@@

<center>Contact: [danielmorillo.ac\@gmail.com](mailto:danielmorillo.ac@gmail.com){.email}</center>
:::::::::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::
:::::::::::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::::

>>>>

:::::: columns
::: {.column width="33%"}
<center>A?</center>

@@

rot_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```
:::

::: {.column width="33%"}
<center>B?</center>

@@

ts_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```
:::

::: {.column width="33%"}
<center>C?</center>

@@

ls_grid +
    geom_point(
    mapping = aes(trait_1, trait_2),
    data    = thetas_transf,
    alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])
  )
```
:::
::::::

@@

<center>Contact: [danielmorillo.ac\@gmail.com](mailto:danielmorillo.ac@gmail.com){.email}</center>
